Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Aceptando cambio de @fergunet
Extending (and improving) MusCRTEP description. Closes #17

\begin{itemize}
\item It offers a central deployment, administration and securing of all mobile devices regardless of their OS. %FERGU: securing como palabra no. security control mejor?
\item It manages and enforces security policies `over the air' for both corporate and employee-owned mobile devices.
\item It does it by enforcing passwords and providing mechanisms for remote lock.
\item It offers the ability to wipe/selective wipe corporate data email/contacts on the device if lost or stolen.
\end{itemize}

@@

The rest of the components are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between client and server sides. 
In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring and acting). This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API will be defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}. On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with. Usually it will be accessed through the operating system (OS). So the type of information to gather from them and also the type of actions to do over them will vary depending on the OS. In most of the cases MUSES could just detect/recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user). This is due to the usual forbiddance or limitation of interactions with other applications that the OSs have. %FERGU: forbiddance parece que existe, pero el corrector me dice que no. Prohibition mejor?

@@

As in the client, there are three main components:
\begin{itemize}
	 \item \textit{System Database}: it stores all the information that the system will manage, including authentication data, enterprise security policies, assets' values, user-related information (trust, context), events data, and, of course, security rules to apply (regarding the security policies).

	 \item \textit{Continuous Real-Time Event Processor (MusCRTEP)}: this component is the core of the MUSES system with respect to the decision making process. It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{EventProcessing_Luckham02,SurveyEventCorrelation_Tiffany02}, gathering the set of occurred events and doing a rule-based threat identification. The output of this module is taken by the \textit{RT2AE}, which also considering information such as trust data and profiles, assets' values, user reputation, or opportunity, performs a risk and trust analysis task \cite{RT2AE_SOTICS13}, and extracts the set of potential rules to consider in the analysed situation. Then, these rules are transformed into decisions (or Device Policies) and submitted to those devices to which they apply.

	 \item \textit{Knowledge Refinement System (MusKRS)}: this module is in charge of analysing the information stored in the system database, identifying relevant data, such as important patterns, key features, or security incidents. These are later processed for tuning up the existing set of rules or for inferring new ones.

>>>>

\begin{itemize}
\item It offers a central deployment, administration and security control of all mobile devices regardless of their OS. %FERGU: securing como palabra no. security control mejor?
%Cambiado
\item It manages and enforces security policies `over the air' for both corporate and employee-owned mobile devices.
\item It does it by enforcing passwords and providing mechanisms for remote lock.
\item It offers the ability to wipe/selective wipe corporate data email/contacts on the device if lost or stolen.
\end{itemize}

@@

The rest of the components are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between client and server sides. 
In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring and acting). This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API will be defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}. On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with. Usually it will be accessed through the operating system (OS). So the type of information to gather from them and also the type of actions to do over them will vary depending on the OS. In most of the cases MUSES could just detect/recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user). This is due to the usual forbiddance or limitation of interactions with other applications that the OSs have. %FERGU: forbiddance parece que existe, pero el corrector me dice que no. Prohibition mejor?
% Yo diría que es forbidding...

@@

As in the client, there are three main components:
\begin{itemize}
	 \item \textit{System Database}: it stores all the information that the system will manage, including authentication data, enterprise security policies, assets' values, user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).

	 \item \textit{Continuous Real-Time Event Processor (MusCRTEP)}: this component is the core of the MUSES system with respect to the decision making process. It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{deliverable21, deliverable52}. This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analyse them to look for an existing security rule that could be applied to the situation. The engine discovers that by analysing the context events which are sent with the user action event, so that a complete model of the risks can be built. The output of this module is an `access request' which is sent to the \textit{RT2AE}. It considers the information included in the access request, as well as other information such as trust data and profiles, assets' values, user reputation, or opportunity, to perform a risk and trust analysis task \cite{RT2AE_SOTICS13}. Finally, the RT2AE extracts the set of potential rules to consider in the analysed situation, and these rules are therefore transformed into decisions (or Device Policies) and submitted to those devices to which they apply.

	 \item \textit{Knowledge Refinement System (MusKRS)}: this module is in charge of analysing the information stored in the system database by means of Data Mining techniques, identifying relevant data, such as important patterns, key features, or security incidents. These are later processed for tuning up the existing set of rules, or for inferring new ones. The KRS component, along with the CRTEP, are what represent the extension of the state of the art in security solutions for a BYOD environment.
